---
title: "music_insights_part_2"
author: "Jerusalem Moore"
date: "11/14/2019"
output: html_document
---

```{r}
library("knitr")
purl("MusicInsights.Rmd", output = "part1.r")
source("part1.r")


```

I'm attempting to find the average rating for each pseudonym I wanted a table that would include every person's entries for each song,
in order to do this I decided to make a separate table only holding the variables I'm worried about(pseudonym and ratings), this is var_table. I found some code on stack overflow that creates an avg column for duplicate rows. Here's the link: https://stackoverflow.com/questions/17383635/average-between-duplicated-rows-in-r. The table holding the pseudonyms with their relative averages is the avg_rating table.

```{r}
library("tidyr")
library("dplyr")
library(data.table)
var_table <- tibble(pseudonym = ratings$pseudonym, ratings = ratings$ratings)
keys <- colnames(var_table)[!grepl('ratings', colnames(var_table))]
X <- as.data.table(var_table)
avg_rating <- X[,list(averageRatings = mean(ratings)), keys]
```

I'm now going to add this newly created column to the person table.
```{r}
person_and_average <-inner_join(avg_rating, person, by="pseudonym")
```

I'm now going to test any predictors of the dpendent variable averageRatings to see if they have any relation. The independent variables being used are the sex, academic_major, academic_level, and year_born
```{r}
library(caret)
set.seed(385)
as.table(as.matrix(person_and_average))
sample_selection <- createDataPartition(person_and_average$averageRatings, p = 0.75, list = FALSE)
train <- person_and_average[sample_selection, ]
test <- person_and_average[-sample_selection, ]
train_model <- lm(averageRatings ~ academic_major + year_born + academic_level + sex, data = person_and_average)
summary(train_model)
predictions <- train_model %>% predict(test)
R2(predictions, test$averageRatings)
MAE(predictions, test$averageRatings)

```

After summarizing the model it seems that the only attribute that seemed to have any relation to averageRatings was whether or not the student was a Computer Information Systems major